An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-27 paper/5.experiments.tex
fix indent + scaled tick

\tab $\putbx{ptail}{s}{v}$ accepts a source list $s$ and a view list $v$ to produce a new list by replacing the tail of $s$ with $v$. $\getbx{ptail}{s}$ return the tail of the source list $s$. The compositions of many $ptail$, in the \textit{put} direction, replace a part of the tail of the source list by the view list, in the \textit{get} direction, returns the such tail from the the source.

\tab $\putbx{bsnoc}{s}{v}$ accepts a source $s$ and a view $v$ as two same length lists, to produce a new list by moving the last element of $v$ to its first position. $\getbx{ptail}{s}$ return another list by moving the first element of the list $s$ to its end position. The compositions of many \textit{ptail}, in the \textit{put} direction, create a permutation of the view list if the source list has a same length with the view, in the \textit{get} direction, produce a permutation of the source list.

\tab \textit{breverse}, is defined in terms of \textit{bFoldr}, a putback function of \textit{foldr} which is an important higher-order function on lists. This program, in the \textit{put} direction, produces a reverse of the view list if the source list has a same length with the view, in the \textit{get} direction, produce a reverse of the source list. \textit{breverse} is more natural than the others since \text{bFoldr} is a Case analysis whose a branch contains a composition $bx_1 \circ bx_2$ where $bx_1$ is a product of a simple function and \textit{bFoldr}. It will look like a composition of more programs at some points in the evaluation if we slow down this process. Note that $\circ$ has a higher priority than $\times$. This leads to seemingly impossible to transform \textit{bReverse} as well as \textit{bFoldr} from the left associative style to the right one.

>>>>

$\putbx{ptail}{s}{v}$ accepts a source list $s$ and a view list $v$ to produce a new list by replacing the tail of $s$ with $v$. $\getbx{ptail}{s}$ return the tail of the source list $s$. The compositions of many $ptail$, in the \textit{put} direction, replace a part of the tail of the source list by the view list, in the \textit{get} direction, returns the such tail from the the source.

$\putbx{bsnoc}{s}{v}$ accepts a source $s$ and a view $v$ as two same length lists, to produce a new list by moving the last element of $v$ to its first position. $\getbx{ptail}{s}$ return another list by moving the first element of the list $s$ to its end position. The compositions of many \textit{ptail}, in the \textit{put} direction, create a permutation of the view list if the source list has a same length with the view, in the \textit{get} direction, produce a permutation of the source list.

\textit{breverse} is defined in terms of \textit{bfoldr}, a putback function of \textit{foldr} which is an important higher-order function on lists. This program, in the \textit{put} direction, produces a reverse of the view list if the source list has a same length with the view, in the \textit{get} direction, produce a reverse of the source list. \textit{breverse} is more natural than the others since \textit{bfoldr} is a Case analysis whose a branch contains a composition $bx_1 \circ bx_2$ where $bx_1$ is a product of a simple function and \textit{bfoldr}. It will look like a composition of more programs at some points in the evaluation if we slow down this process. Note that $\circ$ has a higher priority than $\times$. This leads to seemingly impossible to transform \textit{breverse} as well as \textit{bfoldr} from the left associative style to the right one.
